Diagnosis Visualizations

### 2023-06-08 Diagnosis_Vis.Rmd
Final co-occuring image

tabs
```

```{r}
Mothership_current_Imp$Disorder_Present
CO_OC<- Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .5)+
  scale_size_area(max_size = 30) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Other_Co" = "Other",
                            "No_Co" = "None",
                            "Mood_C" = "Mood",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

CO_OC
```

>>>>

tabs[,5] <- c("Anxiety","BPD","Mood","None","Other","Substance","Trauma")
colnames(tabs)[5] = "Disorder"
tabs
```

```{r}
Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_point(aes(size = ..count..),stat = "bin2d")+
  #scale_size_area(max_size = 30)+
  scale_colour_manual(values = c( "#F4B393","#FC60A8","#7A28CB","#494368"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Other_Co" = "Other",
                            "No_Co" = "None",
                            "Mood_C" = "Mood",
                            "BPD_Co_C" = "BPD",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis")

 "#CEEC97"
 "#F4B393"
 "#FC60A8"
 "#7A28CB"
 "#494368"

```{r}
Mothership_current_Imp %>%
  ggplot(aes(x = Disorder_treat, y = Disorder_Present, color = Disorder_treat)) +
  geom_count(aes(size = after_stat(prop),group = Disorder_treat), alpha = .75)+
 scale_size_area(max_size = 40)+
  scale_colour_manual(values = c("#FE6CAA","#f7a174","#B1D4E0","#A06CFE"))+
  #scale_size_continuous(range = c(10, 30)) +
  theme_classic() +
  theme(axis.text.x = element_text(angle = 45,hjust = 1),
    legend.position = "none") +
  scale_y_discrete(labels=c("Other_Co" = "Other",
                            "No_Co" = "None",
                            "BPD_Co_C" = "BPD",
                            "Trauma_C" = "Trauma", 
                            "Substance_C" = "Substance Use",
                            "Mood_C" = "Mood",
                            "Anxiety_C" = "Anxiety")) +
  labs(title = "Percent of Co Occuring Psychiatric Diosrders per Primary Diagnosis",
    subtitle = "Grouped into subtypes of DSM diagonsis",
    y = "Co-Occuring Psychiatric Disorder",
    x = "Primary Psychiatric Diagnosis") 
```
